\section{Related Work}

\paragraph{Parameter-efficient and quantized adaptation.}
LoRA freezes the pretrained weights and learns low-rank updates to selected projections \citep{hu2021lora}. QLoRA quantizes the frozen base to 4-bit NF4 and back-propagates through it into the LoRA parameters, cutting the memory needed to fine-tune a billion-parameter model by roughly an order of magnitude \citep{dettmers2023qlora}. Recent surveys place these methods within a wider family of parameter-efficient techniques for large models \citep{prottasha2025peft}. We use this recipe without modification. The aim is not a new adaptation method but a complete account of what the standard one costs and yields at the 4~GB limit.

\paragraph{Compact and on-device models.}
A separate line of work targets models small enough to run locally, either by pretraining at reduced scale or by curating higher-quality data \citep{zhang2024tinyllama,gunasekar2023textbooks}; recent surveys catalog these model families and their measured accuracy and efficiency trade-offs \citep{lu2025slmsurvey}. AVA-v2 is not a new base model. It is an adaptation of an existing 2B model, studied under the constraint that the entire process, training through evaluation, happens on one laptop GPU.

\paragraph{Quantized local deployment.}
The llama.cpp project and the GGUF format have made low-VRAM and CPU inference of quantized models routine \citep{gerganov2023llamacpp}. Quality at aggressive quantization is often assumed rather than measured. We give perplexity across an importance-matrix-calibrated ladder so the deployment trade-off is explicit.

\paragraph{Reliability of benchmark evaluation.}
Scores for small models are sensitive to prompt format, few-shot selection, and sample size \citep{biderman2024lessons}, and to overlap between training and evaluation data \citep{tong2026contamination}. We add a concrete case in which a 50-item subset overstated full-set GSM8K accuracy by thirteen points, reported with confidence intervals sized to make such gaps visible.

\paragraph{Inference-time reasoning.}
Chain-of-thought prompting \citep{wei2022cot} and self-consistency \citep{wang2022selfconsistency} raise reasoning accuracy without retraining. We measure the self-consistency gain for AVA-v2 and compare it against an in-model tool-use pathway that rarely activates, and find the former far more effective for this model.
