\documentclass[conference]{IEEEtran}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amssymb}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage[numbers]{natbib}
\usepackage{hyperref}
\usepackage{balance}
\hypersetup{hidelinks}

% Breathing room around floats and captions
\setlength{\textfloatsep}{16pt plus 3pt minus 3pt}
\setlength{\dbltextfloatsep}{18pt plus 3pt minus 3pt}
\setlength{\floatsep}{14pt plus 3pt minus 3pt}
\setlength{\dblfloatsep}{16pt plus 3pt minus 3pt}
\setlength{\intextsep}{14pt plus 3pt minus 3pt}
\setlength{\abovecaptionskip}{8pt}
\setlength{\belowcaptionskip}{4pt}

\title{AVA-v2: A Reproducible Case Study of Adapting and Evaluating a 1.9B Model Under a 2\,GB VRAM Budget on Consumer Hardware}

\author{\IEEEauthorblockN{Muhammad Afsah Mumtaz}
\IEEEauthorblockA{Independent Researcher\\
\texttt{github.com/NAME0x0}\quad\texttt{huggingface.co/NAME0x0}}}

\begin{document}
\maketitle

\begin{abstract}
Open language models have outgrown the hardware most people own. We report an end-to-end case study of adapting and evaluating a compact model within a strict consumer budget. Beginning from Qwen3.5-2B, an approximately two-billion-parameter vision-language model, we fine-tune only its text transformer with 4-bit QLoRA on a single laptop GPU that has 4~GB of memory. Training peaks at 1.81~GB of VRAM, runs for 100 minutes, updates 0.58\% of the parameters, and produces a 42~MB adapter. We evaluate the merged model, which we call AVA-v2, across 17 benchmark configurations covering knowledge, reasoning, mathematics, code, multilingual arithmetic, and instruction following, and report a 95\% Wilson interval for every score. The capability profile is uneven: strong on science and multiple-choice knowledge (ARC-Challenge 82.0\%, ARC-Easy 92.0\%, MMLU 59.2\%) and weak on competition mathematics and strict instruction following. Two results are worth isolating. A 50-question GSM8K estimate of 48\% overstated the full 1{,}319-question result of 35.3\% by about thirteen points, which shows how small subsets can misrepresent compact models. Self-consistency added 8.7 points on GSM8K, whereas an in-model tool-use pathway activated on 0.6\% of problems and changed nothing. The adapter, merged weights, and a quantized GGUF ladder are publicly available.
\end{abstract}

\begin{IEEEkeywords}
QLoRA, parameter-efficient fine-tuning, small language models, low-resource training, model evaluation, quantization.
\end{IEEEkeywords}

\input{sections/01-intro}
\input{sections/02-related}
\input{sections/03-training}
\input{sections/04-data}
\input{sections/05-methodology}
\input{sections/06-results}
\input{sections/07-analysis}
\input{sections/08-deployment}
\input{sections/09-limitations-conclusion}

\appendix
\input{appendix}

\balance
\bibliographystyle{plainnat}
\bibliography{refs}

\end{document}
